---
title: "EventParticipation_Update"
output: html_document
date: "2024-03-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(dplyr)
```

# ++++++++++++ Cross Event ++++++++++++++++ #
```{r}
# using the cross event data #
cross_data <- "/Users/jamesturner/Desktop/Tech Council/Cross-Event_40_Events_Sales_Summary_Excel_93284519469_20240201_2114.xlsx"
cross_data <- read_excel(cross_data)
```

```{r}
# clean cross event data, only left 'event name' and 'event start date' 
cleaned_cross <- cross_data %>%
  select(`Event Name`, `Event Start Date`)
```

```{r}
# remove the part of time, only left date
cleaned_cross$`Event Start Date` <- sub(" .*", "", cleaned_cross$`Event Start Date`)
```

```{r}
# remove the repeat event name
cleaned_cross <- unique(cleaned_cross[, c("Event Name", "Event Start Date")])
```

```{r}
# rename the col names, prepare for merge with CleanedMember.EventParticipation.csv
names(cleaned_cross)[names(cleaned_cross) == "Event Name"] <- "Title"
names(cleaned_cross)[names(cleaned_cross) == "Event Start Date"] <- "Event.Date"
```

```{r}
# change the date formate
cleaned_cross <- cleaned_cross %>%
  mutate(`Event.Date` = as.Date(`Event.Date`, format = "%m/%d/%y"))
```

```{r}
# still change the date formate
cleaned_cross <- cleaned_cross %>%
  mutate(Event.Date = format(as.Date(Event.Date, format = "%m/%d/%y"), "%Y-%m-%d"))
```

```{r}
# This csv contains the event date get from the cross event data
#write.csv(cleaned_cross, file = "CleanedCrossEventDate.csv", row.names = FALSE)
```

# ++++++++++++ CleanedMember.EventParticipation ++++++++++++++++ #
```{r}
Cleaned_eventdate <- read.csv("/Users/jamesturner/Desktop/Tech Council/CleanedMember.EventParticipation.csv")
```

```{r}
# only left the 'Title' (Event name) and 'Event.Date' 
Cleaned_eventdate <- Cleaned_eventdate %>%
  select(`Title`, `Event.Date`)
```

```{r}
# remove repeat variables
Cleaned_eventdate <- unique(Cleaned_eventdate[, c("Title", "Event.Date")])
```

```{r}
# rename...
Cleaned_eventdate$Title <- sub("*** postponed-Hire UP: College & University Recruiting", "Hire UP: College & University Recruiting", Cleaned_eventdate$Title, fixed = TRUE)
```

# ++++++++++++ Cross Event + CleanedMember.EventParticipation ++++++++++++++++ #
```{r}
# merging the event date from cross event data and CleanedMember.EventParticipation data
Merge_Cleaned_eventdate <- merge(Cleaned_eventdate,cleaned_cross, by = c("Title", "Event.Date"), all = TRUE) 
# 365 events 
```

```{r}
Merge_Cleaned_eventdate <- unique(Merge_Cleaned_eventdate[, c("Title", "Event.Date")])
# 365, no repeat event
```

```{r}
# this dataset has all the event dates get from Cross Event dataset and CleanedMember.EventParticipation dataset
write.csv(Merge_Cleaned_eventdate, file = "AllEventDate.csv", row.names = FALSE)
```

# ++++++++++++ Attendee data ++++++++++++++++ #
```{r}
att_data <- "/Users/jamesturner/Desktop/Tech Council/Event Attendees 2018 through 2023.xlsx"
sheet <- excel_sheets(att_data)
att_2018data <- read_excel(att_data, sheet = sheet[1])
att_2019data <- read_excel(att_data, sheet = sheet[2])
att_2020data <- read_excel(att_data, sheet = sheet[3])
att_2021data <- read_excel(att_data, sheet = sheet[4])
att_2022data <- read_excel(att_data, sheet = sheet[5])
att_2023data <- read_excel(att_data, sheet = sheet[6])
```

```{r}
# select the col `Company`, `Title`, `Company Member Type`, `Paid Through`
cleaned_18att <- att_2018data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
cleaned_19att <- att_2019data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
cleaned_20att <- att_2020data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
cleaned_21att <- att_2021data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
cleaned_22att <- att_2022data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
cleaned_23att <- att_2023data %>%
  select(`Company`, `Title`, `Company Member Type`, `Paid Through`)
```

```{r}
# remove the NA 
cleaned_18att <- subset(cleaned_18att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
cleaned_19att <- subset(cleaned_19att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
cleaned_20att <- subset(cleaned_20att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
cleaned_21att <- subset(cleaned_21att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
cleaned_22att <- subset(cleaned_22att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
cleaned_23att <- subset(cleaned_23att, !is.na(`Company Member Type`) & !is.na(`Paid Through`))
```

```{r}
# some repeat, because different people from the same company attend the same event.......
# remove the repeat company name.....
unique_cleaned_23att <- unique(cleaned_23att[, c("Company", "Title", "Paid Through", "Company Member Type")])
unique_cleaned_22att <- unique(cleaned_22att[, c("Company", "Title", "Paid Through", "Company Member Type")])
unique_cleaned_21att <- unique(cleaned_21att[, c("Company", "Title", "Paid Through", "Company Member Type")])
unique_cleaned_20att <- unique(cleaned_20att[, c("Company", "Title", "Paid Through", "Company Member Type")])
unique_cleaned_19att <- unique(cleaned_19att[, c("Company", "Title", "Paid Through", "Company Member Type")])
unique_cleaned_18att <- unique(cleaned_18att[, c("Company", "Title", "Paid Through", "Company Member Type")])
```

```{r}
# merge 1028- 2023 dataset to one dataset
Merge_Cleaned_eventatt <- merge(unique_cleaned_23att, unique_cleaned_22att, by = c("Company", "Title", "Paid Through", "Company Member Type"), all = TRUE)
```

```{r}
Merge_Cleaned_eventatt <- merge(Merge_Cleaned_eventatt, unique_cleaned_21att, by = c("Company", "Title", "Paid Through", "Company Member Type"), all = TRUE)  
Merge_Cleaned_eventatt <- merge(Merge_Cleaned_eventatt, unique_cleaned_20att, by = c("Company", "Title", "Paid Through", "Company Member Type"), all = TRUE)  
Merge_Cleaned_eventatt <- merge(Merge_Cleaned_eventatt, unique_cleaned_19att, by = c("Company", "Title", "Paid Through", "Company Member Type"), all = TRUE)  
Merge_Cleaned_eventatt <- merge(Merge_Cleaned_eventatt, unique_cleaned_18att, by = c("Company", "Title", "Paid Through", "Company Member Type"), all = TRUE)  
```

```{r}
unique_titles <- unique(Merge_Cleaned_eventatt$Title)
unique_title_count <- length(unique_titles)
unique_title_count
# Merge_Cleaned_eventatt has 279 different events
```

# +++++++++++++ Merge event date to the event att dataset based on "Title" +++++++++++++++++ #
```{r}
merged_df <- Merge_Cleaned_eventatt %>%
  left_join(select(Merge_Cleaned_eventdate, Title, Event.Date), by = "Title")
```

```{r}
# this dataset is the cleaned dataset with "Company" "Title" (Event Name), "Paid Through" (Paid Through Date), "Company Member Type", "Event.Date" (Event Date)
#write.csv(merged_df, file = "Att_with_eventdate.csv", row.names = FALSE)
```

```{r}
# Some Event Date are "NA"
# Check how many NA (762)
event_dates_count <- sum(!is.na(merged_df$Event.Date))
print(event_dates_count) # 8621
na_count <- sum(is.na(merged_df$Event.Date))
print(na_count) # 762
```

```{r}
# Check what event does not has the "Event Date"
# 28 events do not has the event date...................
titles_with_na_event_date <- merged_df$Title[is.na(merged_df$Event.Date)]
unique_titles_with_na_event_date <- unique(titles_with_na_event_date)
print(unique_titles_with_na_event_date)
# below 28 events do not has event date information.
```
# Create monthly indicator 

############# FOR EVENT #############

```{r}
merged_df <- na.omit(merged_df)
# 8617 obs
```


```{r}
merged_df <- merged_df %>%
  select(-`Title`)
```


```{r}
# Load the lubridate package for date manipulation
library(lubridate)
# Define the start date
start_date <- as.Date("2018-01-01")
# Define the end date
end_date <- as.Date("2023-12-31")
# Calculate the number of months since start_date for each date in the 'Event.Date' column
merged_df$Month <- 12 * (year(merged_df$Event.Date) - year(start_date)) + month(merged_df$Event.Date) - month(start_date) + 1
```


```{r}
merged_df$Event_Frequency <- 1
# all become one, however, BUT what if a company participates in multiple events in the same month?
```


```{r}
# this way will let the frequency represent the number of times it participates in the event
new_merged_df <- merged_df %>%
  group_by(Company, Month) %>%
  mutate(Event_Frequency = n()) %>%
  distinct(Company, Month, .keep_all = TRUE)
# 7354 obs
```


```{r}
#write.csv(mem_data, file = "/Users/heiyo/Desktop/MQE/Capstone/mem_data.csv", row.names = FALSE)
```


```{r}
mem_data <- read.csv("/Users/jamesturner/Desktop/Tech Council/mem_data_with_noeventandbenefic.csv")
# data from Neel
```


```{r}
# Install the sqldf package from CRAN if you haven't already
install.packages("sqldf")
# Load the sqldf library
library(sqldf)
# Perform a left join operation selecting only the required columns
mem_data <- sqldf("SELECT mem_data.*, new_merged_df.Event_Frequency 
                   FROM mem_data 
                   LEFT JOIN new_merged_df 
                   USING (Month, Company)")
# same 208512 -> correct
```

```{r}
# Replace NA values in the "event_frequency" column with 0
mem_data$Event_Frequency[is.na(mem_data$Event_Frequency)] <- 0
```

################### UPDATE FOR BP ##############

```{r}
install.packages("openxlsx")
```

```{r}
library(openxlsx)
# Specify the file path for the Excel file
#excel_file_path <- "/Users/heiyo/Desktop/MQE/Capstone/mem_data.xlsx"
# Export mem_data as an Excel file
#write.xlsx(mem_data, file = excel_file_path, rowNames = FALSE)
# Provide a message indicating successful export
#cat("mem_data has been exported as an Excel file to:", excel_file_path, "\n")
```

```{r}
# Check if there are any numbers other than 0 in the Event_Frequency column
any_other_than_zero <- any(mem_data$Event_Frequency != 0)
# Print the result
if (any_other_than_zero) {
  cat("There are numbers other than 0 in the Event_Frequency column.\n")
} else {
  cat("There are no numbers other than 0 in the Event_Frequency column.\n")
}
```

```{r}
# Count the number of non-zero values in the Event_Frequency column
non_zero_count <- sum(mem_data$Event_Frequency != 0)
# Print the count
cat("Number of non-zero values in the Event_Frequency column:", non_zero_count, "\n")
```

#Benefit Participants added to mem_data dataset 

```{r}
# Load necessary libraries
library(openxlsx)
benefit_participants <- read.xlsx("/Users/jamesturner/Desktop/Tech Council/BenefitParticipants.xlsx")
# Extract the list of companies that used benefits
benefit_companies <- unique(benefit_participants$Company)
# Create a new column in mem_data called "benefit_usage" initialized with 0
mem_data$Benefit_Usage <- 0
# If appear in BenefitParticipants, = 1
mem_data$Benefit_Usage[mem_data$Company %in% benefit_companies] <- 1
#write.xlsx(mem_data, file = "/Users/heiyo/Desktop/MQE/Capstone/mem_data_with_benefit_usage.xlsx", rowNames = FALSE)
#cat("mem_data with benefit_usage column has been exported as an Excel file.\n")
```

```{r}
# Count the number of occurrences of "1" in the benefit_usage column
num_benefit_users <- sum(mem_data$Benefit_Usage == 1)
#cat("Number of companies using benefits (with benefit_usage = 1):", num_benefit_users, "\n")
```

```{r}
# drop (Erased)
mem_data <- subset(mem_data, Company != "(Erased)")
```

####### CHANGE EVENT FREQUENCY to BINARY #######
```{r}
# 208440 observations
mem_data$Event_Frequency[mem_data$Event_Frequency > 1] <- 1
# Now Event_Frequency becomes binary variable
```

```{r}
# Change the name 'Event_Frequency' to 'Event_Participation'
mem_data <- mem_data %>% 
  rename(Event_Participation = Event_Frequency)
```

######## UPDATE SCORECARD #######
```{r}
scorecard_data <- read.csv("/Users/jamesturner/Desktop/Tech Council/sc_alldata_mems_forcombine.csv")
# 19649 observations
```

```{r}
# Drop useless col
scorecard_data <- scorecard_data %>%
  select(-`SC.Entry.Date`, -`SC.Type`, -`X`)
```

```{r}
# create 'Month' in scorecard
scorecard_data$Month <- 12 * (year(scorecard_data$SC.Date) - year(start_date)) + month(scorecard_data$SC.Date) - month(start_date) + 1
```

```{r}
# check what scorecard 'type' we have
# unique_sctype <- unique(scorecard_data$type)
#  "Business Development" "Outreach"             "Visibility"           "Talent"              
#  "Advocacy"             "Engagement"           "Benefits"             "General" 
```

#### after creating binary col for scorecard, I find that our mem_data has mistake,(a lot of replicating rows, for example Company Name'3Cloud', '4th Source'......) #### ( I didn't realize this issue until I trying to figure out what is the meaning of Payment.Amount, and the month value of those companies are repeated twice. I don't know how to fix it, and it is too late and I got a little bit sore throat.) ####

#### for creating binary col, i tried to create cols such as SC.BusinessDevelopment, SC.Outreach...in scorecard data and then merge to mem_data, but a lot of duplicate cols... therefore, I do each type seperatly.

#### For SC.BusinessDevelopment ####
```{r}
BD_scorecard_data <- scorecard_data %>%
  filter(type == "Business Development") %>%
  mutate(SC.BusinessDevelopment = 1)
# 2256 obs
###### some repeat value appear
###### for example 	
###### 4CTechnologies (Month 45 appear twice, probably because type Business Development has different reasoning)
###### in order to not let mem_data has duplicate obs, I will aggregate BD_scorecard_data
```

```{r}
aggregated_BD_scorecard_data <- BD_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.BusinessDevelopment = sum(SC.BusinessDevelopment)) %>%
  ungroup()
# 1860 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_BD_scorecard_data[, c("Company", "Month", "SC.BusinessDevelopment")], 
                  by = c("Company", "Month"), all.x = TRUE)
# finally............
```

```{r}
# Replace NA values in SC.BusinessDevelopment column with 0
mem_data$SC.BusinessDevelopment <- ifelse(is.na(mem_data$SC.BusinessDevelopment), 0, mem_data$SC.BusinessDevelopment)
```

```{r}
# SC.BusinessDevelopment becomes binary col
mem_data$SC.BusinessDevelopment[mem_data$SC.BusinessDevelopment > 1] <- 1
```

#### For SC.Outreach ####
```{r}
Out_scorecard_data <- scorecard_data %>%
  filter(type == "Outreach") %>%
  mutate(SC.Outreach = 1)
# 10748 obs
```

```{r}
aggregated_Out_scorecard_data <- Out_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Outreach = sum(SC.Outreach)) %>%
  ungroup()
# 7253 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Out_scorecard_data[, c("Company", "Month", "SC.Outreach")], 
                  by = c("Company", "Month"), all.x = TRUE)
# still 208440 obs
```

```{r}
# Replace NA values to 0
mem_data$SC.Outreach <- ifelse(is.na(mem_data$SC.Outreach), 0, mem_data$SC.Outreach)
```

```{r}
mem_data$SC.Outreach[mem_data$SC.Outreach > 1] <- 1
```

#### For SC.Visibility ####
```{r}
Visibility_scorecard_data <- scorecard_data %>%
  filter(type == "Visibility") %>%
  mutate(SC.Visibility = 1)
# 3141 obs
```

```{r}
aggregated_Visibility_scorecard_data <- Visibility_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Visibility = sum(SC.Visibility)) %>%
  ungroup()
# 2656 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Visibility_scorecard_data[, c("Company", "Month", "SC.Visibility")], 
                  by = c("Company","Month"), all.x = TRUE)
# still 208440 obs
```

```{r}
# Replace NA values to 0
mem_data$SC.Visibility <- ifelse(is.na(mem_data$SC.Visibility), 0, mem_data$SC.Visibility)
```

```{r}
mem_data$SC.Visibility[mem_data$SC.Visibility > 1] <- 1
```

#### For SC.Talent ####
```{r}
Talent_scorecard_data <- scorecard_data %>%
  filter(type == "Talent") %>%
  mutate(SC.Talent = 1)
# 1841 obs
```

```{r}
aggregated_Talent_scorecard_data <- Talent_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Talent = sum(SC.Talent)) %>%
  ungroup()
# 1517 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Talent_scorecard_data[, c("Company", "Month", "SC.Talent")], 
                  by = c( "Company","Month"), all.x = TRUE)
# still 208440 obs
```

```{r}
# Replace NA values to 0
mem_data$SC.Talent <- ifelse(is.na(mem_data$SC.Talent), 0, mem_data$SC.Talent)
```

```{r}
mem_data$SC.Talent[mem_data$SC.Talent > 1] <- 1
```

#### For SC.Advocacy ####
```{r}
Advocacy_scorecard_data <- scorecard_data %>%
  filter(type == "Advocacy") %>%
  mutate(SC.Advocacy = 1)
# 924 obs
```

```{r}
aggregated_Advocacy_scorecard_data <- Advocacy_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Advocacy = sum(SC.Advocacy)) %>%
  ungroup()
# 872 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Advocacy_scorecard_data[, c("Company", "Month", "SC.Advocacy")], 
                  by = c( "Company", "Month"), all.x = TRUE)
# still 208440 obs
```

```{r}
# Replace NA values to 0
mem_data$SC.Advocacy <- ifelse(is.na(mem_data$SC.Advocacy), 0, mem_data$SC.Advocacy)
```

```{r}
mem_data$SC.Advocacy[mem_data$SC.Advocacy > 1] <- 1
```

#### For SC.Engagement ####
```{r}
Engagement_scorecard_data <- scorecard_data %>%
  filter(type == "Engagement") %>%
  mutate(SC.Engagement = 1)
# 118 obs
```

```{r}
aggregated_Engagement_scorecard_data <- Engagement_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Engagement = sum(SC.Engagement)) %>%
  ungroup()
# 116 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Engagement_scorecard_data[, c("Company", "Month", "SC.Engagement")], 
                  by = c( "Company","Month"), all.x = TRUE)
# still 208440 obs
```

```{r}
# Replace NA values to 0
mem_data$SC.Engagement <- ifelse(is.na(mem_data$SC.Engagement), 0, mem_data$SC.Engagement)
```

```{r}
mem_data$SC.Engagement[mem_data$SC.Engagement > 1] <- 1
```

#### For SC.Benefits ####
```{r}
Benefits_scorecard_data <- scorecard_data %>%
  filter(type == "Benefits") %>%
  mutate(SC.Benefits = 1)
# 232 obs
```

```{r}
aggregated_Benefits_scorecard_data <- Benefits_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.Benefits = sum(SC.Benefits)) %>%
  ungroup()
# 201 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_Benefits_scorecard_data[, c("Company", "Month", "SC.Benefits")], 
                  by = c("Company", "Month"), all.x = TRUE)
```

```{r}
# Replace NA values to 0
mem_data$SC.Benefits <- ifelse(is.na(mem_data$SC.Benefits), 0, mem_data$SC.Benefits)
```

```{r}
mem_data$SC.Benefits[mem_data$SC.Benefits > 1] <- 1
```

#### For SC.General ####
```{r}
General_scorecard_data <- scorecard_data %>%
  filter(type == "General") %>%
  mutate(SC.General = 1)
# 389 obs
```

```{r}
aggregated_General_scorecard_data <- General_scorecard_data %>%
  group_by(Company, Month) %>%
  summarise(SC.General = sum(SC.General)) %>%
  ungroup()
# 309 obs
```

```{r}
mem_data <- merge(mem_data, aggregated_General_scorecard_data[, c("Company", "Month", "SC.General")], 
                  by = c("Company", "Month"), all.x = TRUE)
```

```{r}
# Replace NA values to 0
mem_data$SC.General <- ifelse(is.na(mem_data$SC.General), 0, mem_data$SC.General)
```

```{r}
mem_data$SC.General[mem_data$SC.General > 1] <- 1
```

```{r}
write.csv(mem_data,"mem_data_eventbenefitscorecard.csv")
```


```{r}
# Load required libraries for survival analysis
#install.packages("survival")
library(survival)

# Load your dataset
final_data <- read.csv("/Users/jamesturner/Desktop/Tech Council/final_data.csv")  

# Create a new dataset where each row represents a company for each month
expanded_data <- expand.grid(Company = unique(final_data$Company),
                              Month = 1:72)  # Assuming you have 72 months of data
expanded_data <- merge(expanded_data, final_data, by = c("Company", "Month"), all.x = TRUE)

# Replace missing values in Member_Status with 0 (indicating not a member)
expanded_data$Member_Status[is.na(expanded_data$Member_Status)] <- 0

# Sort the dataset by Company and Month
expanded_data <- expanded_data[order(expanded_data$Company, expanded_data$Month), ]

# Create a new column to represent the status transition from 1 to 0
expanded_data$Event <- ifelse(expanded_data$Member_Status == 1 & c(0, head(expanded_data$Member_Status, -1)) == 0, 1, 0)

# Create the survival object
surv_obj <- Surv(time = expanded_data$Month, event = expanded_data$Event)

# Fit a survival model using Cox proportional hazards regression
surv_model <- coxph(surv_obj ~ Event_Participation + Benefit_Usage + SC.BusinessDevelopment + SC.Outreach + SC.Visibility + SC.Talent + SC.Advocacy + SC.Engagement + SC.Benefits + SC.General, data = expanded_data)

# Summary of the survival model
summary(surv_model)
```
#All Features Graph

```{r}
# Load required libraries
library(dplyr)
library(ggplot2)

# Assuming 'final_data' is your data frame

# Step 1: Filter rows where Member_Status transitions from 1 to 0
transition_rows <- final_data %>%
  filter(Member_Status == 1 & lead(Member_Status) == 0)

# Step 2: Calculate percentage of companies using each feature one, two, three, and four years before the transition
# Assuming Event_Participation, Benefit_Usage, SC.BusinessDevelopment, etc. are columns in your DataFrame

# Function to calculate percentage of companies using a feature
calculate_percentage <- function(feature, data) {
  one_year_before <- mean(data[data$Month %in% (transition_rows$Month - 12), ][[feature]])
  two_years_before <- mean(data[data$Month %in% (transition_rows$Month - 24), ][[feature]])
  three_years_before <- mean(data[data$Month %in% (transition_rows$Month - 36), ][[feature]])
  four_years_before <- mean(data[data$Month %in% (transition_rows$Month - 48), ][[feature]])
  return(c(one_year_before, two_years_before, three_years_before, four_years_before))
}


# Calculate percentages for each feature
features <- c("Event_Participation", "Benefit_Usage", "SC.BusinessDevelopment", "SC.Outreach",
              "SC.Visibility", "SC.Talent", "SC.Advocacy", "SC.Engagement", "SC.Benefits", "SC.General")

percentages <- sapply(features, function(feature) {
  calculate_percentage(feature, final_data)
})


# Step 3: Plot the results
# Prepare data for plotting
plot_data <- data.frame(
  Feature = rep(features, each = 4),
  Period = rep(c("One Year Before", "Two Years Before", "Three Years Before", "Four Years Before"), times = length(features)),
  Percentage = c(percentages)
)

# Convert 'Period' to factor with appropriate levels and reverse the order
plot_data$Period <- factor(plot_data$Period, levels = rev(c("One Year Before", "Two Years Before", "Three Years Before", "Four Years Before")))

# Define custom color palette for better discernibility
custom_colors <- c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#FFF533", "#A65628", "#F781BF", "#999999", "#66CCCC")

# Plot with custom colors and reversed x-axis, and y-axis as percentage
ggplot(plot_data, aes(x = Period, y = Percentage * 100, color = Feature)) +
  geom_point() +
  geom_line() + # Add a line between the dots
  labs(x = "", y = "Percentage of Usage", title = "% of Member Usage Before Leaving PTC") +
  theme_minimal() +
  theme(legend.position = "right") +
  scale_color_manual(values = custom_colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```



```{r}
# Load required libraries
library(dplyr)
library(ggplot2)

# Assuming 'final_data' is your data frame

# Step 1: Filter rows where Member_Status transitions from 1 to 0
transition_rows <- final_data %>%
  filter(Member_Status == 1 & lead(Member_Status) == 0)

# Step 2: Calculate percentage of companies using each feature one, two, three, and four years before the transition
# Assuming Event_Participation, Benefit_Usage, SC.BusinessDevelopment, etc. are columns in your DataFrame

# Function to calculate percentage of companies using a feature for those with Member_Status = 1 for longer than 48 months
calculate_percentage_long_term <- function(feature, data) {
  long_term_members <- data %>%
    filter(Member_Status == 1 & Month <= max(transition_rows$Month) - 48)  # Filter companies with Member_Status = 1 for longer than 48 months
  
  percentage <- mean(long_term_members[[feature]])
  
  return(percentage)
}

# Calculate percentages for each feature
features <- c("Event_Participation", "Benefit_Usage", "SC.BusinessDevelopment", "SC.Outreach",
              "SC.Visibility", "SC.Talent", "SC.Advocacy", "SC.Engagement", "SC.Benefits", "SC.General")

percentages_long_term <- sapply(features, function(feature) {
  calculate_percentage_long_term(feature, final_data)
})

# Step 3: Plot the results
# Prepare data for plotting
plot_data_long_term <- data.frame(
  Feature = features,
  Percentage_Long_Term = percentages_long_term
)

# Plot
ggplot(plot_data_long_term, aes(x = Feature, y = Percentage_Long_Term)) +
  geom_bar(stat = "identity", fill = "green") +
  labs(x = "Feature", y = "Percentage of Usage", title = "% of Member Usage for Companies with Member_Status = 1 for > 48 Months") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



#Feautures with Small Percentages 

```{r}

# Step 1: Filter rows where Member_Status transitions from 1 to 0
transition_rows <- final_data %>%
  filter(Member_Status == 1 & lead(Member_Status) == 0)

# Step 2: Calculate percentage of companies using each feature one, two, three, and four years before the transition
# Assuming Event_Participation, Benefit_Usage, SC.BusinessDevelopment, etc. are columns in your DataFrame

# Function to calculate percentage of companies using a feature
calculate_percentage <- function(feature, data) {
  one_year_before <- mean(data[data$Month %in% (transition_rows$Month - 12), ][[feature]])
  two_years_before <- mean(data[data$Month %in% (transition_rows$Month - 24), ][[feature]])
  three_years_before <- mean(data[data$Month %in% (transition_rows$Month - 36), ][[feature]])
  four_years_before <- mean(data[data$Month %in% (transition_rows$Month - 48), ][[feature]])
  return(c(one_year_before, two_years_before, three_years_before, four_years_before))
}

# Calculate percentages for each feature
features <- c("Event_Participation", "Benefit_Usage", "SC.BusinessDevelopment", "SC.Outreach",
              "SC.Visibility", "SC.Talent", "SC.Advocacy", "SC.Engagement", "SC.Benefits", "SC.General")

percentages <- sapply(features, function(feature) {
  calculate_percentage(feature, final_data)
})

# Prepare data for plotting
plot_data <- data.frame(
  Feature = rep(features, each = 4),
  Period = rep(c("One Year Before", "Two Years Before", "Three Years Before", "Four Years Before"), times = length(features)),
  Percentage = c(percentages)
)

# Convert 'Period' to factor with appropriate levels and reverse the order
plot_data$Period <- factor(plot_data$Period, levels = rev(c("One Year Before", "Two Years Before", "Three Years Before", "Four Years Before")))

# Define features with small percentages
small_percentage_features <- c("SC.BusinessDevelopment", "SC.Visibility", "SC.Talent", "SC.Advocacy", "SC.Engagement", "SC.Benefits", "SC.General")

# Filter plot_data for small percentage features
plot_data_small <- plot_data %>% filter(Feature %in% small_percentage_features)

# Define custom color palette for better discernibility
custom_colors <- c("#4DAF4A", "#984EA3", "#FF7F00", "#FFFF33", "#A65628", "#999999", "#66CCCC")

# Plot for small percentage features with custom colors and y-axis as percentage
ggplot(plot_data_small, aes(x = Period, y = Percentage * 100, color = Feature)) +
  geom_point() +
  geom_line() + # Add a line between the dots
  labs(x = "", y = "Percentage of Usage", title = "% of Member Usage Before Leaving PTC (Small Percentage Features)") +
  theme_minimal() +
  theme(legend.position = "right") +
  scale_color_manual(values = custom_colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```










